Improving \textsl{Gaia} parallax precision \\ with a data-driven model of stars

### 2017-06-06 paper/paper.tex
typo

  By modeling the selection function in detail, one could improve the quality of the inferred \cmb, its effect on individual objects, and its connection to physical models of the Milky Way. 

>>>>

  By modeling the selection function in detail, one could improve the quality of the inferred \cmd, its effect on individual objects, and its connection to physical models of the Milky Way. 
